### 2019-08-04 thesis.tex
*** empty log message ***

\chapter{Final remarks}
\label{cha:final}
In this text, we have summarized the early results of the analysis of a new first
principles theory, depicted in \Cref{noneigenmode}, which combines collective
processes (eigenmodes) and collisional interactions (noneigenmodes), for Langmuir
and ion-sound waves, without any \emph{ad hoc} addition. The importance of this
formalism, became clear right in the first study, presented in \Cref{coll-damp},
where it was shown the collisional damping rate calculated with the heuristic
Spitzer formula, that is independent of the wave-number, is highly overestimated
when compared with the rigorous expression, which has to be integrated in the
wave-number space. The Spitzer approximation is largely applied to the modeling
and interpretation of several solar phenomena observed by space-probes \cite{
  VWK2000,Hannah2009,ZVST11,KRB12,KF13,RR14,Reid2015}, a fact that emphasizes
the necessity of the development of a mathematically rigorous theory able to
describe hybrid situations involving collective oscillations and collisional
interactions.

@@

Since the pervasiveness of the plasma state in space came as a fact, plasma
physics became an essential component in the multidisciplinary framework of
astrophysics. At the same time, observations of space plasma phenomena have
been gaining increasing relevance in the advance of theoretical, computational,
and experimental plasma physics research \cite{Kulsrud2005}. This mutual contribution is
driven by solar physics.

>>>>

\chapter{Final remarks}
\label{cha:final}
In this text, we have summarized the early results of the analysis of a new first
principles theory, depicted in \Cref{noneigenmode}, which combines collective
processes (eigenmodes) and collisional interactions (noneigenmodes), for Langmuir
and ion-sound waves, without any \emph{ad hoc} addition. The importance of this
formalism, became clear right in the first study, presented in \Cref{coll-damp},
where it was shown the collisional damping rate calculated with the heuristic
Spitzer formula, that is independent of the wave-number, is highly overestimated
when compared with the rigorous expression, which has to be integrated in the
wave-number space. The Spitzer approximation is largely applied to the modeling
and interpretation of several solar phenomena observed by space-probes \cite{
  Vinas2000,Hannah2009,ZVST11,KRB12,KF13,RR14,Reid2015}, a fact that emphasizes
the necessity of the development of a mathematically rigorous theory able to
describe hybrid situations involving collective oscillations and collisional
interactions.

@@

Since the pervasiveness of the plasma state in space came as a fact, plasma
physics became an essential component in the multidisciplinary framework of
astrophysics. At the same time, observations of space plasma phenomena have
been gaining increasing relevance in the advance of theoretical\cite{YZKS16,
  Tigik2017b}, computational\cite{Donnert2014,Pezzi2018}, and experimental
\cite{Howes2018,Peterson2019} plasma physics research.
